---
output:
  pdf_document:
    template: template.tex
    latex_engine: xelatex
    number_sections: yes
mainfont: "Roboto"
fontsize: 11pt

title: '`r get_meta(meta_vec, "title")`'
datetime: '`r get_meta(meta_vec, "datetime")`'

classoption:
  - letterpaper
  - oneside
graphics: null
geometry: margin=1.0in
shaded_quote: no
colorlinks: yes
# lof: yes
# lot: yes
toc: yes

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE, echo = FALSE, warning = FALSE, fig.align="center"}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
```

```{r wrap-hook}
library("knitr")
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x <- knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x <- strwrap(x, width = n)
    x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})
```

# BioCompute Object Domain Entries

## Top Level Fields

```{r, linewidth = 60}
get_tlf() %>% convert_json()
```

## Provenance Domain

```{r, linewidth = 60}
get_provenance() %>% convert_json()
```

## Usability Domain

```{r, linewidth = 60}
get_usability() %>% convert_json()
```

## Extension Domain

```{r, linewidth = 60}
get_extension() %>% convert_json()
```

## Description Domain

```{r, linewidth = 60}
get_description() %>% convert_json()
```

## Execution Domain

```{r, linewidth = 60}
get_description() %>% convert_json()
```

## Parametric Domain

```{r, linewidth = 60}
get_description() %>% convert_json()
```

## Input/Output Domain

```{r, linewidth = 60}
get_io() %>% convert_json()
```

## Error Domain

```{r, linewidth = 60}
get_error() %>% convert_json()
```

\clearpage

# Funding

The Seven Bridges Cancer Genomics Cloud has been funded in whole or in part with Federal funds from the National Cancer Institute, National Institutes of Health, Contract No. HHSN261201400008C and ID/IQ Agreement No. 17X146 under Contract No. HHSN261201500003I.

# References

Lau et al. (2017) The Cancer Genomics Cloud: Collaborative, Reproducible, and Democratized --- A New Paradigm in Large-Scale Computational Research. Cancer Res. 77(21):e3-e6. doi: 10.1158/0008-5472.CAN-17-0387.

\clearpage

# Appendix 1: BioCompute Object Specification v1.3.0

```{r echo=FALSE, warning=FALSE}
suppressMessages(library("kableExtra"))

gen_bco_kable <- function(dframe, name_header) {
  dframe %>%
    dplyr::select(-Domain) %>%
    dplyr::select(-Optional) %>%
    kable(format = "latex", longtable = TRUE, booktabs = TRUE, linesep = "") %>%
    kable_styling(
      latex_options = c("striped", "hold_position", "repeat_header"),
      full_width = FALSE, position = "center", font_size = 8
    ) %>%
    column_spec(1:2, width = "4cm") %>%
    column_spec(3, width = "8cm") %>%
    kableExtra::group_rows("Top Level Fields", 1, 4) %>%
    kableExtra::group_rows("Provenance Domain", 5, 15) %>%
    kableExtra::group_rows("Usability Domain", 16, 16) %>%
    kableExtra::group_rows("Extension Domain", 17, 19) %>%
    kableExtra::group_rows("Description Domain", 20, 23) %>%
    kableExtra::group_rows("Execution Domain", 24, 32) %>%
    kableExtra::group_rows("Parametric Domain", 33, 33) %>%
    kableExtra::group_rows("Input and Output Domain", 34, 36) %>%
    kableExtra::group_rows("Error Domain, acceptable range of variability", 37, 37)
}

dframe <- read.table("bco-spec.csv", header = TRUE, sep = ";")
gen_bco_kable(dframe, "")
```

\clearpage

# Appendix 2: The Complete BioCompute Object

```{r}
get_bco_json()
```
